Compositional equivalences based on Open pNets

### 2021-10-01 2016-Weak-FH-Bisim/WeakBisim.tex
a new abstract

pNets is a generalisation of automata that includes variables and hierarchical composition. Open pNets are pNets with holes, i.e. placeholders inside the hierarchical structure  that can be filled by sub-systems. Reasoning on open pNets allows us to reason on open systems.
  Open pNets have a notion of \emph{synchronised actions}
  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
  in Lotos).

This article defines bisimulation relations  for the comparison of systems specified as pNets.
 We first define a strong bisimulation for open pNets.
  In practice, as happens in process algebras, strong bisimulation is too strong, and
  we need to define some coarser relations, taking into account
  invisible or internal moves.
  We then define an equivalence relation similar to
  the classical \emph{weak bisimulation}, and study its properties.
Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
\end{abstract}

>>>>

pNets is a generalisation of automata that model open systems. They features variables and hierarchical composition. Open pNets are pNets with holes, i.e. placeholders inside the hierarchical structure  that can be filled by sub-systems. 
%  Open pNets have a notion of \emph{synchronised actions}
%  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
%  in Lotos).

This article defines bisimulation relations  for the comparison of systems specified as pNets.
 We first define a strong bisimulation for open pNets.
  In practice, as happens in process algebras, strong bisimulation is too strong, and
  we define some coarser relations, taking into account
  invisible or internal moves.
  We then define an equivalence relation similar to
  the classical \emph{weak bisimulation}, and study its properties.
Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
We identify sufficient conditions on the automata to ensure compositionality of strong and weak bisimulation.
The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
\end{abstract}
